### 2018-12-14 README.Rmd
rm old research qs
no figures in README
experiment with collapsible chunks

* LAGOS
    * Lake depth
    * IWS area
    * IWS/Lake area
* Cropland Data Layer
    * IWS pasture types (forage or not)
    * IWS specific crops (corn, wheat, etc.)
    * IWS crop frequency/rotation
* gSSURGO
    * IWS wetland potential (as a proxy for tile drainage)
    * IWS soil organic carbon
    * IWS root zone depth
    * IWS lithology (sand %, clay %, etc.)
* USGS
    * IWS from county - manure, fertilizer, and deposition of N,P

@@

* Is ag intensification related to changes in lake water quality?
    * Maybe areas with reduced intensification have been improving?
* Do ag conservation practices affect lake water quality?
* Others?

@@

```{r maps, echo=FALSE}
knitr::include_graphics("figures/rmd-hi_ag_iws_w_ep-1.png")
```

>>>>

<details><summary><b>Lake Characteristics</b> (`LAGOSNE`) </summary><p>

* [x] Lake depth
* [x] IWS area
* [x] IWS/Lake area
</p></details>

* Cropland Data Layer
    * IWS pasture types (forage or not)
    * IWS specific crops (corn, wheat, etc.)
    * IWS crop frequency/rotation
* gSSURGO
    * IWS wetland potential (as a proxy for tile drainage)
    * IWS soil organic carbon
    * IWS root zone depth
    * IWS lithology (sand %, clay %, etc.)
* USGS
    * IWS from county - manure, fertilizer, and deposition of N,P

@@

@@
